%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Architect \& Product Manager} % Job title
    {Delta Electronics} % Organization
    {Taipei City, Taiwan} % Location
    {May 2019 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Established a cross-region project team with 10+ members to research and develop an edge computing solution in manufacturing industry.}
        \item {Designed a microservice software architecture for edge computing solution to enable flexiblity and scalibility.}
        \item {Adopted gitlab-CI and Ansible to deploy microservices in Kubernetes cluster to minize deployment efforts.}
        \item {Developed a tensorflow serving like interface library in Golang.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Technical Lead} % Job title
    {} % Organization
    {} % Location
    {Feb. 2018 - May 2019 (1 year 4 months)} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Established a corss-region team of engineers, designers and QA with 20+ members in charge of front-end development.}
        \item {Implemented working model for cross team collaboration and guidelines for engineers and designers.}
        \item {Led team to develop over 10 applications at the same time, 2 of them attract hundreds of users internally and improve work performance.}
        \item {Implemeted API microservices with ExpressJS and deployed as AWS Lambda functions.}
        \item {Incubated 3 senior developers to become team leaders leading regional team members.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Technical Lead} % Job title
    {} % Organization
    {} % Location
    {Apr. 2016 - Feb. 2018 (1 year 11 months)} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Established a team of engineers with 9+ members in charge of innovative software research and development.}
        \item {Defined and promoted in-house UI framework to all front-end developers.}
        \item {Designed and built up CI/CD pipelines with gitlab, gitlab-CI, docker, ansible and more.}
        \item {Designed and deployed applications to AWS cloud environment}
        \item {Implemented RESTful API guideline to enable consistent API design across applications.}
        \item {Led and implemented 3 projects with React and promoted to organization to boost work performance}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Project Engineer} % Job title
    {} % Organization
    {} % Location
    {Sep. 2014 - Apr. 2016 (1 year 8 months)} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Member of Strategy and Innovation Research team which was under CTO to research for enterprise transformation.}
        \item {Developed application prototypes with React to demonstrate concepts to Delta senior managers (incl. CEO, CTO and COO) and got positive feedback in both 2015 and 2016.}
        \item {Operated 2 internal projects which transfers to BU/BG after incubation stage. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Internship} % Job title
    {IKV Technology} % Organization
    {Taipei City, Taiwan} % Location
    {Sep. 2013 - Aug. 2014 (1 year)} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented Bitcoin wallet related features.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Internship} % Job title
    {ETS-Lindgren} % Organization
    {Taipei City, Taiwan} % Location
    {Mar. 2011 - May 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Rewrote and enhanced signal processing algorithm and implement GUI in C\#.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
