%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Side Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Owner} % Role
    {ffmpeg.js} % Title
    {https://github.com/ffmpegjs/ffmpeg.js} % Location
    {Oct. 2019 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {ffmpeg.js is a pure Webassembly / Javascript port of FFmpeg. It enables video \& audio record, convert and stream right inside browsers.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Contributor} % Role
    {Tesseract.js} % Title
    {https://github.com/naptha/tesseract.js} % Location
    {Feb. 2018 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Tesseract.js is a pure Javascript port of the popular Tesseract OCR engine. It supports over 100 languages, automatic text orientation and script detection, a simple interface for reading paragraph, word, and character bounding boxes. Tesseract.js can run either in a browser and on a server with NodeJS.}
        \item {20k+ stars in Github.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Developer} % Role
    {VCLink Web Development} % Title
    {https://vclink.com/} % Location
    {Sep 2018 – Feb 2019} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {VCLink is a co-investment platform built by VSC Ecosystem (VSC) where qualified investors can co-invest alongside VSC and trusted anchor VCs in carefully selected early-stage deals.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Owner} % Role
    {FGO Calculator} % Title
    {https://github.com/jeromewu/fgo-calc} % Location
    {Feb 2018 – May 2018} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {A calculator helps you to calculate the overall resource left in events.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
