%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{false}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
\name{Wen-Chieh Wu}{}
\position{Technical Lead{\enskip\cdotp\enskip}Software Engineer}
% \address{42-8, Bangbae-ro 15-gil, Seocho-gu, Seoul, 00681, Rep. of KOREA}

\mobile{(+886) 932986206}
\email{jeromewus@gmail.com}
\homepage{jeromewu.github.io}
\github{jeromewu}
\linkedin{wenchiehwu}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
\medium{jeromewus}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}

% \quote{``Before you are a leader, success is all about growing yourself. When you become a leader, success is all about growing others.'' - Jack Welch}

%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Grab}
  {　}
% The date on the letter, default is the date of compilation
\letterdate{}
% The title of the letter
\lettertitle{Job Application for Engineering Manager}
% How the letter is opened
\letteropening{}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Resume}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {}
  %{Wen-Chieh Wu~~~·~~~Cover Letter}
  {Wen-Chieh Wu}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
Passionate problem solver, enthusiastic about software technologies, team leader with over 3 years of experience in innovative software solution development and manufacturing industry in an international environment.

Coordinate over 10 internal application development projects and play as an architect in software system architecture design. Excel in leadership, critical thinking, communication and software engineering. Strong skills in JavaScript (incl. React, React-Native, Redux, ES6), major contributor of tesseract.js (16.9k+ stars on Github) now.

\lettersection{Why Grab?}
Grab impresses me deeply in business localization and agility from my own experience, and I would like to join Grab and benefit more people with trouble in transportation.

The first time I met Grab was in Singapore Zoo, looking for a taxi to go back to hotel, I installed Grab in my ASUS Android phone and it crashes right away. Few months later when I was in Cambodia, looking for a taxi again. It took more than 10 USD for hotel to arrange a taxi which is quiet expensive, so we looked for an alternative and found out GrabTukTuk. I remembered that it crashed on my phone months ago, but I gave it a try with the same phone again and it worked perfectly.

There are two aspects suprised me, one is Grab's deep localization as users are able to book TukTuk in Cambodia, another is the quality of Grab Android app.\ as the engineering team is able to fix the bugs in an unpopular Android phone. Both leave me great impressions and that's why I would like to join Grab and benefit more people with trouble in transportation.

\lettersection{Why Me?}
With solid technical skills and years of leading engineering team collaborating with cross-functional teams to develop various projects, I believe I am capable of operating with enthusiasm and flexibility in a fast-paced, constantly evolving team environment. I think that is exactly the challenge of being an engineering manager in Grab.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
